Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-11-07 Article.tex
Modification and finalization of the AR model

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab: HSparameters}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5954.043$ & $-3.358\times10^{-3}$ & $2.641\times10^{-1}$ & $-8.678\times10^{-2}$ & $2.269\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.216\times10^{-4}$ & $-5.613\times10^{-2}$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab: HSparameters}
\end{tabular}
\end{table}

@@

To obtain the constitutive equation, it is necessary to determine all the parameters $A$, $Q$ $\alpha$ and $n$ for a given material. 
The strain has a significant non-linear influence on the behavior of the material by the mechanism of strain hardening and softening at high values of deformation. 
A compensation in strain must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
\begin{equation}
A(\varepsilon) = \exp{\left[\ln A_0 + \ln A_1\varepsilon + \ln A_2\varepsilon^2 + \ln A_3\varepsilon^3 + \cdots + \ln A_m\varepsilon^m\right]}
\label{eq:ArA}
\end{equation}
\begin{equation}
Q(\varepsilon) = Q_0 + Q_1\varepsilon + Q_2\varepsilon^2 + Q_3\varepsilon^3 + \cdots + Q_m\varepsilon^m
\label{eq:ArQ}
\end{equation}
\begin{equation}
\alpha(\varepsilon) = \alpha_0 + \alpha_1\varepsilon + \alpha_2\varepsilon^2 + \alpha_3\varepsilon^3 + \cdots + \alpha_m\varepsilon^m
\label{eq:Aralpha}
\end{equation}
\begin{equation}
n(\varepsilon) = n_0 + n_1\varepsilon + n_2\varepsilon^2 + n_3\varepsilon^3 + \cdots + n_m\varepsilon^m
\label{eq:Arn}
\end{equation}

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization. The values $\ln A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method. This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates. Equation (\ref{eq:ArStress}) is finally used: 
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

The following part shows the calculation procedures of these material constants at $\varepsilon = 0.1$ as example. 
Taking the natural logarithm of Equations (\ref{eq:ARmodel1}) and (\ref{eq:ARmodel2}), the following relationships can be obtained:
\begin{equation}
\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}
\end{equation}
\begin{equation}
\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}
\end{equation}
From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon)$  and $\sigma^y = f(\ln\mdot\varepsilon)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$. 
It should be noted that later in this document all values of strain will be taken into account.
\includegraphics[width=0.9\columnwidth]{Figures/LnAlp}
\caption{Relationship between $\ln \sigma^y$ and $\ln \dot{\varepsilon}^p$}
\label{fig:LnAlp}
\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE0}
\caption{Relationship between $\sigma^y$ and $\ln \dot{\varepsilon}^p$}
\label{fig:LnSinhE0}
The values of those parameters are therefore equal to $n_1=6.78177$ and $\beta=0.150563$ ($\alpha=\beta/n_1 = 0.0222011$).
From Equation (\ref{eq:ARmodel}), the following relationship can be obtained:
\begin{equation}
\label{eq:lnSinh}
\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}
\end{equation}
By applying the chain derivative rule, we get the following relationship to calculate the energy activation coefficient $Q$.
\begin{equation}
\label{eq:parQ}
Q = R\left[\frac{\partial \ln \mdot\varepsilon}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
\end{equation}
From Equation (\ref{eq:lnSinh}) and Equation (\ref{eq:parQ}) we can deduce the parameters $n_2 $ and $Q $ from the slopes of the functions $\ln \sinh(\alpha\sigma^y) = f(\ln \dot{\varepsilon}^p)$ and $\ln \sinh(\alpha\sigma^y) = g(1/T)$ as shown in Figure \ref{fig:LnSinhE} and Figure \ref{fig:LnSinhT}. 
Thus those values are $4.94273$ and $437.385\ KJ.mol^{-1}$ respectively.
\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE}
\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $\ln \dot{\varepsilon}^p$}
\label{fig:LnSinhE}
\includegraphics[width=0.9\columnwidth]{Figures/LnSinhT}
\caption{Relationship between $\ln \sinh(\alpha\sigma^y) $ and $1/T$}
\label{fig:LnSinhT}
As these coefficients are calculated for a single strain value as example, it is possible to take into account their dependence on all strain values. 
Hence the need to find a function for each coefficient for all temperatures and strains. 
Figure  \ref{fig:ARparameters} shows the relationships between $\alpha$, $Q$, $n_2$, $\ln A$ and true strain $\varepsilon^p$ for AISI P20 alloy using leasquare method. 
For each parameter (whose strain dependant expressions are given by Equations \ref{eq:alpha}, \ref{eq:Q}, \ref{eq:n} and \ref{eq:lnA}), the values of constants are summarized in Table \ref{tab: ARparameters}. 
Figure \ref{fig:iCorrelationAR} is the comparison of predicted values of AR model and experimental values where the correlaton is good. 
The gap between experimental and prediction is small. 
But for the strain rate $\mdot\varepsilon = 0.01\ \ps$ and for the two low temperatures values, the AR model is not able to predict the softening.
\begin{equation}
\label{eq:alpha}
\alpha(\varepsilon^p) = \alpha_0 + \alpha_1\varepsilon^{{p^1}} + \alpha_2\varepsilon^{p^2} + \alpha_3\varepsilon^{p^3} + \alpha_4\varepsilon^{p^4} + \alpha_5\varepsilon^{p^5} + \alpha_6\varepsilon^{p^6}
\end{equation}
\begin{equation}
\label{eq:Q}
Q(\varepsilon^p) = Q_0 + Q_1\varepsilon^{{p^1}} + Q_2\varepsilon^{p^2} + Q_3\varepsilon^{p^3} + Q_4\varepsilon^{p^4} + Q_5\varepsilon^{p^5} + Q_6\varepsilon^{p^6}
\end{equation}
\begin{equation}
\label{eq:n}
n_2(\varepsilon^p) = n_{20} + n_{21}\varepsilon^{{p^1}} + n_{22}\varepsilon^{p^2} + n_{23}\varepsilon^{p^3} + n_{24}\varepsilon^{p^4} + n_{25}\varepsilon^{p^5} + n_{26}\varepsilon^{p^6}
\end{equation}
\begin{equation}
\label{eq:lnA}
\ln A(\varepsilon^p) = \ln A_0 + \ln A_1\varepsilon^{{p^1}} + \ln A_2\varepsilon^{p^2} + \ln A_3\varepsilon^{p^3} + \ln A_4\varepsilon^{p^4} + \ln A_5\varepsilon^{p^5} + \ln A_6\varepsilon^{p^6}
\end{equation}
\includegraphics[width=1.02\columnwidth]{Figures/ARparameters}
\caption{Relationships between $\alpha$ (a)  , $Q$ (b) , $n_2$ (c)  and $lnA$ (d)  with the plastic strain $\varepsilon^p$ by polynomial functions}
\label{fig:ARparameters}
\caption{Parameters' constants of Arrhenius Model}
\begin{tabular}{lllll}
&					  &				      &				        &\\
Parameters&$\alpha$   &$Q (MJ.mol^{-1})$ &$n_2$                &$\ln A$\\
&					  &				      &				        &\\
&$\alpha_0 = 0.03702$ & $Q_0 = 0.454825$  & $n_{20} = 4.49273$  & $\ln A_0 = 34.7431$\\
&$\alpha_1 =-0.301107$& $Q_1 = -0.450492$ & $n_{21}=15.2803$    & $\ln A_1 =-36.826$\\
&$\alpha_2 = 2.19877$ & $Q_2=4.76922 $    & $n_{22} =-170.126$  & $\ln A_2 =393.423$\\
Values&$\alpha_3=-8.30819$&$Q_3 =-31.6016$& $n_{23} =651.241$   & $\ln A_3 =-2611.42$\\
&$\alpha_4 = 16.823$  & $Q_4 = 89.8821$   & $n_{24} =-1225.15$  & $\ln A_4 =7436.98$\\
&$\alpha_5 =-17.2732$ & $Q_5 =-113.829$   & $n_{25} =1143.54$   & $\ln A_5 =-9426.54$\\
&$\alpha_6 =7.04342$  & $Q_6 = 53.3699$   & $n_{26} =-423.066$  & $\ln A_6 =4422.49$\\
\label{tab: ARparameters}
{Figures/CompExpAR}
\caption{Comparison between the experimental and predicted flow stresses by AR model}
\label{fig:iCorrelationAR}
\subsection{PTM model\label{sec:ProposedModel}}
The PTM model is a generalized formulation of the MZA model. 
Indeed, the shortcomings of the MZA model are taken into account in this formulation, which makes the model flexible for any type of studied material as it does not require a limited number of parameters. The intrinsic functions of the model, which are the polynomial type functions, will determine the parameters of the model according to the degree of the polynomial, which provides a good fit for each function. The equation describing the PTM model is therefore given by.
\begin{equation}
\label{eq:PTM-model}
\sigma^y(\varepsilon^p,\mdot\varepsilon,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}. Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material. The larger these quantities are, the more parameters need to be identified for the PTM model.
The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}. Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.

>>>>

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{llllllc}
\hline
$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HSparameters}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5954.043$ & $-3.358\times10^{-3}$ & $2.641\times10^{-1}$ & $-8.678\times10^{-2}$ & $2.269\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.216\times10^{-4}$ & $-5.613\times10^{-2}$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab:HSparameters}
\end{tabular}
\end{table}

@@

To obtain the constitutive equation, it is necessary to determine all the parameters $A$, $Q$ $\alpha$ and $n$ for a given material. 
The strain has a significant non-linear influence on the behavior of the material by the mechanism of strain hardening and softening at high values of deformation. 
A compensation in strain must therefore be taken into account in the Arrhenius model, which leads to the definition of the modified Arrhenius model for which the $A$, $Q$ $\alpha$ and $n$ parameters are expressed as a function of the strain $\varepsilon$ by means of polynomial functions of degree $m$ (varying from $1$ to $9$) of the form:
\begin{equation}
A(\varepsilon) = \exp{\left[\ln\!A_0 + \ln\!A_1\varepsilon + \ln\!A_2\varepsilon^2 + \ln\!A_3\varepsilon^3 + \cdots + \ln\!A_m\varepsilon^m\right]}
\label{eq:ArA}
\end{equation}
\begin{equation}
Q(\varepsilon) = Q_0 + Q_1\varepsilon + Q_2\varepsilon^2 + Q_3\varepsilon^3 + \cdots + Q_m\varepsilon^m
\label{eq:ArQ}
\end{equation}
\begin{equation}
\alpha(\varepsilon) = \alpha_0 + \alpha_1\varepsilon + \alpha_2\varepsilon^2 + \alpha_3\varepsilon^3 + \cdots + \alpha_m\varepsilon^m
\label{eq:Aralpha}
\end{equation}
\begin{equation}
n(\varepsilon) = n_0 + n_1\varepsilon + n_2\varepsilon^2 + n_3\varepsilon^3 + \cdots + n_m\varepsilon^m
\label{eq:Arn}
\end{equation}

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization. 
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method. 
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:ARparameters}. 
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
\begin{tabular}{llll}
\hline
$\alpha_i~(\text{MPa}^{-1})$ & $Q_i~(\text{MJ.mol}^{-1})$ & $\ln\!A_i~(\ps)$ & $n_i$\\
\hline
$\alpha_0=0.0392$ & $Q_0=0.467$ & $\ln\!A_0=35.8092$ & $n_0=4.8216$ \\
$\alpha_1=-0.4092$ & $Q_1=-0.6516$ & $\ln\!A_1=-58.8219$ & $n_1=3.2813$ \\
$\alpha_2=3.9229$ & $Q_2=7.6084$ & $\ln\!A_2=740.3302$ & $n_2=71.5963$ \\
$\alpha_3=-20.713$ & $Q_3=-48.016$ & $\ln\!A_3=-5049.2979$ & $n_3=-1956.1871$ \\
$\alpha_4=62.1376$ & $Q_4=66.795$ & $\ln\!A_4=11305.3573$ & $n_4=14460.9217$ \\
$\alpha_5=-99.9999$ & $Q_5=468.8898$ & $\ln\!A_5=20220.008$ & $n_5=-54309.8814$ \\
$\alpha_6=58.7108$ & $Q_6=-2303.1535$ & $\ln\!A_6=-153871.1135$ & $n_6=117612.0374$ \\
$\alpha_7=54.3688$ & $Q_7=4370.6566$ & $\ln\!A_7=317981.5396$ & $n_7=-148819.8996$ \\
$\alpha_8=-99.9999$ & $Q_8=-3939.3826$ & $\ln\!A_8=-297254.899$ & $n_8=102387.2537$ \\
$\alpha_9=42.5233$ & $Q_9=1397.0283$ & $\ln\!A_9=107585.17$ & $n_9=-29621.1293$ \\
\hline
\label{tab:ARparameters}
\end{tabular}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates. 
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$: 
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

Figure \ref{fig:iCorrelationAR} shows the comparison of the values predicted by the Arrhenius model and the experimental values. 
The difference between the experimental and predicted values is small. 
But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpAR}
\caption{Comparison between the experimental and predicted flow stresses by AR model}
\label{fig:iCorrelationAR}
\end{figure}
\FloatBarrier
%-------------------------------------------------------------------------
\subsection{PTM model\label{sec:ProposedModel}}
%--------------------------------------------------------------------------
The PTM model is a generalized formulation of the MZA model. 
Indeed, the shortcomings of the MZA model are taken into account in this formulation, which makes the model flexible for any type of studied material as it does not require a limited number of parameters. The intrinsic functions of the model, which are the polynomial type functions, will determine the parameters of the model according to the degree of the polynomial, which provides a good fit for each function. The equation describing the PTM model is therefore given by.
\begin{equation}
\label{eq:PTM-model}
\sigma^y(\varepsilon^p,\mdot\varepsilon,T) = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}. Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material. The larger these quantities are, the more parameters need to be identified for the PTM model.
The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}. Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.
